Compilation With Program Synthesis

### 2023-08-22 new-paper/introduction.tex
a small fix
formatting

We have developed a first-order functional programming language, \Pika, which will compile to SSL specifications. \SuSLik{} can then take these SSL specifications and generate \SuSLang. Finally, the resulting \SuSLang{} code can be converted to C and then run. In addition to this translational semantics, we also provide a standard abstract machine semantics for \Pika{} and use this to show correctness of the translation into SSL.

@@

  \item In order to provide seamless interoperability between SSL and \Pika, we provide a separation between algebraic datatypes and their representation in memory.
    At a type-level, we track this representation in memory. Furthermore, we describe a kind of polymorphism over memory layouts of an algebraic datatype. (Section~\ref{sec:layouts})

>>>>

We have developed a  functional programming language, \Pika, which will compile to SSL specifications. \SuSLik{} can then take these SSL specifications and generate \SuSLang. Finally, the resulting \SuSLang{} code can be converted to C and then run. In addition to this translational semantics, we also provide a standard abstract machine semantics for \Pika{} and use this to show correctness of the translation into SSL.

@@

  \item In order to provide seamless interoperability between SSL and \Pika, we provide a mechanism to related algebraic data types to their representation in memory. In particular, Pika has a language construct that allows the programmer to define a kind of function from values of an algebraic data type to SSL assertions. This is called a \textit{layout}. (Section~\ref{sec:layouts})

### 2023-08-22 new-paper/layouts.tex
formatting

>>>>

These functions should be injective, as the translator should be able to distinguish between the different constructors of the algebraic data type value exclusively using the SSL assertions. This injectivity requirement is not enforced by the compiler. Also, the choice of arrow in the layout type declaration syntax \lstinline[language=Pika]{L : T >-> layout[x]} is motivated by this requirement, since this kind of double-headed arrow is traditionally used for injective functions.
